Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-10-18 manuscript/manuscript_preprint.Rmd
updates preprint formatting

---
bibliography: ~/Dropbox/Bibliography/MicroMeso.bib
csl: components/ecology.csl
fontsize: 12pt
geometry: margin=1in
header-includes:
- \usepackage{lineno}
- \linenumbers
- \usepackage{setspace}
- \usepackage{sectsty}
- \doublespacing
- \usepackage{todonotes}
- \usepackage[document]{ragged2e}
- \usepackage{times}
- \usepackage{enumitem}
- \usepackage{color, soul}
layout: 12pt
linkcolor: black
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
  word_document: default
urlcolor: black
---

@@

\textbf{Running head:} Demographic data and population forecasting

\textbf{Word count:} 8039 (including captions and reference list)

\textbf{Corresponding author:}  
Andrew Tredennick (atredenn@gmail.com)  
Department of Wildland Resources and the Ecology Center  
5230 Old Main Hill  
Utah State University  
Logan, Utah 84322, USA

Last compile: \today

@@

@@

\vspace{-3em}
\begin{align}
y_{i,q,t}^{S} &\sim \text{Bernoulli}(s_{i,q,t}), \\
\text{logit}(s_{i,q,t}) &= \beta_{0,t} + \beta_{s,t}x_{i,q,t} + \beta_{Q,q} + \textbf{z}'_t \boldsymbol{\beta}_c + \beta_{d,1} w_{i,t} + \beta_{d,2} (x_{i,q,t}w_{i,q,t}),
\end{align}
\vspace{-3em}

@@

\vspace{-3em}
\begin{align}
y_{i,q,t+1}^G &\sim \text{Normal}(\mu_{i,q,t+1}, \sigma^2_{x_{i,q,t+1}}), \\
\mu_{i,q,t+1} &= \beta_{0,t} + \beta_{s,t}x_{i,q,t} + \beta_{Q,q} + \textbf{z}'_t \boldsymbol{\beta}_c + \beta_{d,1} w_{i,q,t} + \beta_{d,2} (x_{i,q,t}w_{i,q,t}),
\end{align}
\vspace{-3em}

@@

\vspace{-3em}
\begin{align}
\sigma^2_{x_{i,q,t+1}} = a \, \text{exp}[b \times \mu_{i,q,t+1}],
\end{align}
\vspace{-3em}

@@

\vspace{-3em}
\begin{align}
y^{R}_{q,t+1} \sim \text{NegBin}(\lambda_{q,t+1},\phi),
\end{align}
\vspace{-3em}

@@

\vspace{-3em}
\begin{align}
\lambda_{q,t+1} = \tilde{c}_{q,t} \, \text{exp}\left(\beta_{0,t} + \beta_{Q,q} + \textbf{z}'_t \boldsymbol{\beta}_c + \beta_{d}\sqrt{\tilde{c}_{q,t}}\right),
\end{align}
\vspace{-3em}

@@

\vspace{-3em}
\begin{align}
\tilde{c}_{q,t} = pc_{q,t} + (1-p)\bar{c}_{Q,t},
\end{align}
\vspace{-3em}

@@

\vspace{-3em}
\begin{align}
y_{q,t+1}^{P} &\sim \text{LogNormal}(\mu_{q,t+1}, \sigma^2)_{0}^{1}, \\
\mu_{q,t+1} &= \beta_{0,t} + \beta_{s,t}x_{q,t} + \beta_{Q,q} + \textbf{z}'_t \boldsymbol{\beta}_c,
\end{align}
\vspace{-3em}

@@

\vspace{-3em}
\begin{align}
\text{lppd}_{\text{CV}} = \sum_{t=1}^T \text{log}_e \int [y_{t,\text{hold}}|\theta][\theta|y_{\text{train}}]d\theta,
\end{align}
\vspace{-3em}

@@

\vspace{-3em}
\begin{align}
\sum_{t=1}^T \text{log}_e \left(\frac{1}{S} \sum^S_{s=1}[y_{t,\text{hold}}|\theta_{ts}]  \right).
\end{align}
\vspace{-3em}

@@

\vspace{-3em}
\begin{align}
n(v_{j},t+1) = \int_{L_{j}}^{U_{j}} k_{j}(v_{j},u_{j},\bar{w_{j}}(u_{j}))n(u_{j},t)du_{j},
\end{align}
\vspace{-3em}

@@

\vspace{-3em}
\begin{align}
k_{j}(v_{j},u_{j},\bar{w_{j}}) = S_j(u_j, \bar{w_{j}}(u_{j}))G_j(v_{j},u_{j},\bar{w_{j}}(u_{j})) + R_j(v_{j},u_{j},\bar{w_{j}}),
\end{align}
\vspace{-3em}

@@

@@

\singlespace{}

>>>>

---
bibliography: ~/Dropbox/Bibliography/MicroMeso.bib
csl: components/ecology.csl
fontsize: 11pt
geometry: margin=1in
header-includes:
- \usepackage{sectsty}
- \usepackage{todonotes}
- \usepackage{times}
- \usepackage{enumitem}
- \usepackage{color, soul}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \chead{\color{red}\textsf{MANUSCRIPT IN PRESS AT \emph{METHODS IN ECOLOGY AND EVOLUTION}}}
- \lhead{}
- \rhead{}
layout: 11pt
linkcolor: black
output:
  pdf_document:
    fig_caption: yes
    keep_tex: no
  word_document: default
urlcolor: black
---

\thispagestyle{fancy}

@@

@@

\twocolumn

@@

\begin{align}
y_{i,q,t}^{S} &\sim \text{Bernoulli}(s_{i,q,t}), \\
\text{logit}(s_{i,q,t}) &= \beta_{0,t} + \beta_{s,t}x_{i,q,t} + \beta_{Q,q} + \textbf{z}'_t \boldsymbol{\beta}_c \\
&+ \beta_{d,1} w_{i,t} + \beta_{d,2} (x_{i,q,t}w_{i,q,t}),
\end{align}

@@

\begin{align}
y_{i,q,t+1}^G &\sim \text{Normal}(\mu_{i,q,t+1}, \sigma^2_{x_{i,q,t+1}}), \\
\mu_{i,q,t+1} &= \beta_{0,t} + \beta_{s,t}x_{i,q,t} + \beta_{Q,q} + \textbf{z}'_t \boldsymbol{\beta}_c \\
&+ \beta_{d,1} w_{i,q,t} + \beta_{d,2} (x_{i,q,t}w_{i,q,t}),
\end{align}

@@

\begin{align}
\sigma^2_{x_{i,q,t+1}} = a \, \text{exp}[b \times \mu_{i,q,t+1}],
\end{align}

@@

\begin{align}
y^{R}_{q,t+1} \sim \text{NegBin}(\lambda_{q,t+1},\phi),
\end{align}

@@

\begin{align}
\lambda_{q,t+1} = \tilde{c}_{q,t} \, \text{exp}\left(\beta_{0,t} + \beta_{Q,q} + \textbf{z}'_t \boldsymbol{\beta}_c + \beta_{d}\sqrt{\tilde{c}_{q,t}}\right),
\end{align}

@@

\begin{align}
\tilde{c}_{q,t} = pc_{q,t} + (1-p)\bar{c}_{Q,t},
\end{align}

@@

\begin{align}
y_{q,t+1}^{P} &\sim \text{LogNormal}(\mu_{q,t+1}, \sigma^2)_{0}^{1}, \\
\mu_{q,t+1} &= \beta_{0,t} + \beta_{s,t}x_{q,t} + \beta_{Q,q} + \textbf{z}'_t \boldsymbol{\beta}_c,
\end{align}

@@

\begin{align}
\text{lppd}_{\text{CV}} = \sum_{t=1}^T \text{log}_e \int [y_{t,\text{hold}}|\theta][\theta|y_{\text{train}}]d\theta,
\end{align}

@@

\begin{align}
\sum_{t=1}^T \text{log}_e \left(\frac{1}{S} \sum^S_{s=1}[y_{t,\text{hold}}|\theta_{ts}]  \right).
\end{align}

@@

\begin{align}
n(v_{j},t+1) = \int_{L_{j}}^{U_{j}} k_{j}(v_{j},u_{j},\bar{w_{j}}(u_{j}))n(u_{j},t)du_{j},
\end{align}

@@

\begin{align}
k_{j}(v_{j},u_{j},\bar{w_{j}}) &= S_j(u_j, \bar{w_{j}}(u_{j}))G_j(v_{j},u_{j},\bar{w_{j}}(u_{j})) \\
&+ R_j(v_{j},u_{j},\bar{w_{j}}),
\end{align}

@@

\onecolumn

@@
